\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments

\usepackage{rotating} % for sideway table
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{cleveref}

\usepackage{array,tabularx}
  
\usepackage{float}
\restylefloat{table}

% bibliography
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{}{,} % no comma between author and year

\title{APSI Summer Research Grant Proposal\\
The political determinants of FDI quality in China}
\author{Anh Le \\
Department of Political Science, Duke University}


\begin{document}
\maketitle

\section{Motivation: The quality of FDI is crucial to China's growth, but we do not understand it well}

Foreign Direct Investment (FDI) plays a central role in China's economic miracle. As one of the first signs of reform, in 1979 China allowed foreign enterprises to enter the country with the Sino-foreign joint venture law. In 1980, China established four coastal specialized economic zones (SEZs) in its southeast.\footnote{Zhuhai, Shenzhen, Shantou in Guangdong Province, and Xiamen in Fujian Province, all situated close to the capitalist Macao, Hong Kong, and Taiwan.} These are the laboratories of capitalism that demonstrated the benefits of capitalism and added political fuel to further liberalization \citep[sec 1]{Gallagher2002}.

Today, the foreign sector continues to play a big role in China's economy, accounting for over half of China's exports and imports. The foreign sector is also highly productive. It provides for 30\% of industrial output and generates 22\% of industrial profits while employing only 10\% of the labor force \citep{WorldBank2010}.

As its initial period of fast growth wanes, China has shifted its focus from the quantity of incoming FDI to its quality. For growth to continue, China needs FDI to bring not just capital but also technological innovation into the economy to improve its productivity. Importantly, Chinese officials hope that when FDI firms will come into contact with Chinese firms and create technological spillover by allowing Chinese firms to imitate or absorb foreign technology.

While the quality of FDI is crucial to China's future growth, we still do not understand why some localities have better FDI while others don't. The economics literature has examined the economic determinants of FDI quality (e.g. provinces' level of development, labor force quality, etc.), but none has looked at the political determinants \citep{Wei2012, Cheung2004}. This approach stands in stark contrast with the earlier studies of China's economic liberalization. We have learned that it was the political incentives of officials that determined their interest in attracting FDI \citep{Shirk1993}. From that lesson, our understanding of what determines the quality of FDI should also be politically sophisticated.

\section{Theory: Officials with short time horizon favors corrupt FDI. Officials with long time horizon favors high quality FDI.}

The \textit{time horizon} of an official determines how much they care about the future. An official with a short time horizon wants immediate benefits. In contrast, an official with a long time horizon cares about the payoff in the future.

I hypothesize that officials want FDI for two competing reasons: 1) the bribes that foreign firms bring,\footnote{Some scholars have suggested that foreign firms receive favorable treatments from the governments, potentially due to their bribes \citep{Huang2011}.} and 2) the technological spillover to domestic firms. An official with a short time horizon does not want to wait for the technological spillover to materialize in the years to come. Therefore, they would favor corrupt FDI for the immediate benefits. In contrast, an official with a long time horizon wants to attract high quality of FDI.

\section{Research methodology}

To investigate whether an official's time horizon changes their preference for corrupt vs high-quality FDI, I need to 1) measure their time horizon, and 2) measure their preference for corrupt FDI.

I will complete both task with a survey module of Chinese local officials, included in the \textit{Creating Human Resource Systems and Enhancing Government Performance Survey}. The survey is conducted by Beijing University's Institute for Quantitative Methods in collaboration with local party and government offices. The respondents are prefecture-level officials from party and government offices that participate in policy and expenditure decisions.

\textbf{Measuring time horizon.} To measure time horizon, I check how close the official is to their mandated retirement age. The closer to the retirement, I expect the official to have shorter time horizon and more preference for corrupt FDI.

\textbf{Measuring preference for corrupt FDI.} Given that no one would admit to their own corruption, to measure this preference I will rely on a survey conjoint experiment. This technique allows the researcher to tease out the preference of the officials by presenting two hypothetical FDI projects and asking the officials to indicate which one is preferable. We make the two options non-sensitive by randomizing the characteristics of the projects so that it is not clear we are focusing on corruption \citep{Hainmueller2014}.

To proxy for corrupt FDI, I use how much land the project will need. This is because FDI projects need to ask for land-use rights from local officials, a process that is highly susceptible to bribery \citep{USChamberofCommerce2012}. In addition, given the scarcity of land and the contentious nature of forced land acquisition for development, there is no reason for an official to favor a FDI project with large land requirement other than corruption \citep{AmnestyInternational2012}.

\section{Implementation plan}

The cost of one module in the survey is \$5,000, which I will share with Fengming Lu, a fellow PhD student in Political Science. Fengming is currently in China. He has contacted and acquired the consent of the survey's Principal Investigator.

I will travel to Beijing this May in order to finalize the survey questions and the survey sample with the survey team. Depending on the permission of the survey team, I may also be able to travel along with the enumerators to interview Chinese prefecture officials.



\clearpage
\bibliographystyle{chicago}
\bibliography{library}
\end{document}
